BoRA: Bayesian Hierarchical Low-Rank Adaption for Multi-task Large Language Models

### 2024-06-13 paper/main.tex
Updates from Overleaf

\title{BoRA: Hierarchical Bayesian Low-Rank Adaption for Multi-task Large Language Models}
\author[1]{Simen Eide}
\author[2]{Arnoldo Frigessi}
\affil[1]{University of Oslo, Schibsted}
\affil[1]{University of Oslo}
\date{March 2024}

@@

BoRA addresses these trade-offs by leveraging a Bayesian hierarchical model that allows tasks to share information through global hierarchical prior parameters. This enables tasks with limited data to benefit from the overall structure derived from related tasks while allowing tasks with more data to specialize. We demonstrate the effectiveness of BoRA on the next token generation task using the Talk of Norway Dataset, where each parliament representative's speeches represent distinct tasks. Our experimental results show that BoRA outperforms both traditional individual and unified model approaches, achieving lower perplexity and better generalization across tasks. This method provides a scalable and efficient solution for multi-task LLM finetuning, with significant practical implications for diverse applications such as media content generation, chatbot responses, and scriptwriting.
}

\section{Introduction}
Large Language Models (LLM) have become a popular model for solving a wide range of generative text problems. LLMs are typically pretrained on a large and diverse dataset of texts, and then fine-tuned on a new data set of texts, dedicated to a specific task. The fine-tuning process is often done by maximizing the next token log likelihood of the task-specific dataset, and the resulting model is then used to make predictions and generations on new data. A popular fine-tuning method is Low-Rank Adaption (LoRA), which reduces the number of trainable parameters by a factor of up to 10'000 and the GPU memory requirement by a factor of 3, while still outperforming other finetuning techniques (\cite{hu_lora_2022}).

When performing fine-tuning of LLMs, the practitioner often wants to solve multiple similar tasks at the same time: 
A media organization might want to use an LLM to generate various textual elements to generate headlines, keywords, and summaries for a given news article. 
A website might have multiple chatbot tasks answering questions to their users handling inquiries across a range of topics such as product information, order status, and troubleshooting.
And finally, a scriptwriting AI might want to generate dialogues for different characters in a movie, each with their unique style and vocabulary.

In these multi-task cases, the practitioner can either (1) train one model for each task and dataset separately, or (2) train one model for all tasks and condition the specific output wanted (e.g \cite{Raffel2019}).
There is a trade-off between these two approaches: Train each task separately and the model will be able to specialize on each task, but it may suffer from limited data available for each task. Train one model for all tasks, and the model will be able to share information between tasks, but it may not be able to specialize on each task due to limited model capacity.

In this paper we suggest a way to circumvent these trade-offs and presents a generalization of the two LoRA fine-tuning methods for multi-task problems, which we call Hierarchical Bayesian Low-Rank Adaption method (BoRA).
The Hierarchical LoRA method allows tasks to share information between each other through sharing a set of global hierarchical prior parameters, in a Bayesian hierarchical setting. 
This means that tasks with little data can benefit from the global structure of the related tasks, while tasks with more data can specialize on their specific task.
We show in Section \ref{sec:BoRA} that BoRA can be seen as a generalization of the two approaches above.

To test our method, we evaluate the Hierarchical LoRA method on the next token generation problem of parliament speeches letting each parliament representative be a task. In our setting, BoRA is superior to both conventional approaches above and suggest a way to mitigate the trade-off between the two.
% Write something about how easy it is to implement and how it can be used in practice?

The paper is organized as follows: Section \ref{sec:related_works} presents related works, Section \ref{sec:method} presents the Hierarchical LoRA method, Section \ref{sec:experimental_setup} describes the experimental setup, Section \ref{sec:results} presents the results, and Section \ref{sec:discussion} discusses the results and the implications of the Hierarchical LoRA method.

@@

\section{Related works} \label{sec:related_works}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\subsection{Finetuning methods}
A popular approach to finetuning neural networks involves adjusting only the top layer (or the n top layers) of a pre-trained neural network (e.g. \cite{yosinski_how_2014}). These techniques observe that features learned in the lower layers of the network are general and transferable, while the top layers are more task-specific. This approach has been widely adopted in neural networks. However, in this paper we focus on the LoRA method, which instead allows us to train a low rank decomposition of the entire network.

There are several variations of the LoRA algorithm. The Sparse Mixture of Low Rank Adapters (SIRA) \cite{zhu_sira_2023}, for instance, creates a Mixture of Expert on the low-rank parameters. Another variation, the Weight Decomposed Low-Rank Adaption (DoRA) \cite{hayou_lora_2024}, decomposes the low-rank parameters into scale and unit norm direction parameters. There is also the Efficient Low Rank Adaption (LoRA+) \cite{hayou_lora_2024}, which improves the existing LoRA optimization algorithm by adjusting the learning rate of the low-rank parameters.
All these methods are designed to improve the performance of the LoRA algorithm, and can be used in conjunction with the proposed Hierarchical LoRA method.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Method: Hierarchical LLM} \label{sec:method}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
This section describes the Hierarchical LoRA method for multi-task problems. We start by defining the task and data structure, and then introduce the pretrained autoregressive language model. We then describe the LoRA method, and finally present our Hierarchical LoRA model.

\subsection{Task and Data Structure}
We define our study across $D$ distinct tasks, denoted as $d=1,2,...,D$. For each task $d$, we have a dataset $\mathcal{D}_d$ containing $N_d$ documents, with each document consisting of a sequence of $W_n$ tokens, $n=1,..., N_d$. This dataset structure can be formally represented as:

\begin{equation} \label{eq:data}
\mathcal{D} = \{ \mathcal{D}_d \}_{d=1}^D  =  \{ \{ w_{d,n,1:W_n} \}_{n=1}^{N_d} \}_{d=1}^D
\end{equation}
%
In this notation, $w_{d,n,1:W_n}$ represents the token sequence in the $n^{th}$ document of the $d^{th}$ task. For simplification in subsequent discussions, we will omit the indices $d$ and $n$ when their reference is evident from the context.

@@

\subsection{The Hierarchical Bayesian LoRA model} \label{sec:BoRA}
In the hierarchical LoRA model, we introduce a LoRA parameter set for each task $d$, denoted as $\theta_d$, containing all the low-rank decomposition matricies $A_d$ and $B_d$ from each decomposed layer in the Large Language Model. The likelihood of the data $\mathcal{D}$ given the task parameters $\theta_{1:D}$ is then given by (combining equation \ref{eq:data} and \ref{eq:LLMprob}):

\begin{align}  \label{eq:lik}
    & \text{L}(\mathcal{D} | \theta_1, \theta_2, \ldots, \theta_D) = \prod_{d=1}^D L(\mathcal{D}_d | \theta_d) \nonumber \\
    &= \prod_{d=1}^D \prod_{n=1}^{N_d} \prod_{i=1}^{W_n-1} \text{LLM}(w_{d,n,i+1} | w_{d,n,1:i}; \theta_d).
\end{align}
%
%
Tasks will share some knowledge with each other, and we model this by introducing a Gaussian hierarchical prior over the task parameters $\theta_{1:D}$, given by
\begin{equation} \label{eq:prior}
    P(\theta_{1:D} | \Theta, \tau ) = \prod_{d=1}^D N(\theta_d ; \Theta, \frac{1}{\tau} I)
\end{equation}
%
where $\Theta$ is a set of hierarchical mean parameters, $I$ is a unit diagonal matrix and $\tau \geq 0$ is a scalar precision hyperparameter controlling how similar the task parameters $\theta_d$ should be to the hierarchical mean parameters $\Theta$.
We let $\Theta$ have a uniform hyperprior (i.e. $P(\Theta) = 1$). The prior assumes that the task parameters share the common origin from the shared Gaussian prior, because the tasks are related: input data come from similar distributions and the output tasks has similar aspects. 
The precision hyperparameter $\tau$ controls how much the task parameters $\theta_d$ are a priori expected to be allowed to deviate from the hierarchical mean parameters $\Theta$. 
This is essentially a measure for how much structure and information the tasks share with each other, and should be set by the practitioner based on her's prior knowledge.

@@

The resulting BoRA model balances each task based on its data size and similarity to the other tasks: If a task has few data points, the posterior in equation \ref{eq:posterior} will be dominated by the prior term and the task parameters will be close to the global hierarchical parameters and borrow information and structure from these. On the other hand, if a task has a lot of data points, the likelihood will dominate the posterior and the task parameters will be allowed to learn more about the specific task and rely less on the hierarchical parameters.

@@

\subsection{Optimization}
Given a precision hyperparameter $\tau$, we want to find the maximum a posteriori (MAP) estimate of the hierarchical model. 
We will do this by using AdamW (\cite{adamW}), a gradient-based optimization algorithm, optimizing over the task parameters $\theta_{1:D}$ and the hierarchical mean parameters $\Theta$ using the posterior in equation \ref{eq:posterior}.
This implies that the task parameters with have gradients both towards minimizing the convential LLM loss (represented by the likelihood term) and the hierarchical mean parameters (originating from the prior). The hierarchical mean parameters $\Theta$ will have gradients towards the average of the task parameters, and learn to represent the global structure of the tasks.

@@

    \centering
    \resizebox{\linewidth}{!}{%
    \includegraphics[width=\textwidth]{figures/training_lengths.png}
    }
    \caption{Number of training examples for each task}
    \label{fig:task_len}
\end{figure}
% As base model, use opt-350m as it is predominantly trained on English, and only has seen a small amount of Norwegian data from the commoncrawls dataset.
To test our method, we optimize the model with a range of different precision hyperparameters $\tau$, and evaluate the models' Perplexity on the test set for each task.
% DEF PERPLEXITY
Perplexity is defined as the exponentiated average negative log-likelihood per token, and is a common metric for evaluating language models. A lower perplexity indicates a better model.
We use the Talk of Norway Dataset~\cite{lapponi_talk_2018}, which consists of speeches of Norwegian parliament politicians.
Each speaker will come from different political parties and geographical areas, but the tasks will still share a common domain. 
Therefore, we can consider different speakers of this dataset as different tasks. Specifically, we select chronologically the 25 first speakers that have above 100 speeches in the dataset.
This gives us a total of 25 tasks with samples ranging from 110 to 477 documents, and an average of 202 documents per task. For some speakers we have significantly less data as for others. 
The distibution of samples per task can be seen in Figure~\ref{fig:task_len}.
We leave 33\% of the data for the test set.

@@

We find no relationship between dataset size and the final perplexity (Figure \ref{fig:absolute_improvement}). One could expect that tasks with more data are able to learn more about their specific task and achieve a lower perplexity, but this is not the case in our experiments. There are many other task specific factors such as under-represented dialects and political views that can influence the final perplexity. Controlling for these factors is difficult and out of scope for this paper, but we believe that these factors may be the reason for this negative result.

@@

%% MCMC vs MAP
In principle, one could bypass the Maximum a Posteriori maximization and adopt a fully Bayesian approach which would tell us how much we can trust the hierarchical model. Such an approach  would require the use of Markov Chain Monte Carlo, Variational Inference or other methods.
This would allow us to sample from the posterior distribution of the hierarchical model, and obtain uncertainty estimates for the task parameters.
However, MCMC methods are computationally heavy, and it is not clear to us how to best sample from the posterior distribution of the language model in an efficient and scalable way.
A middle ground between a full bayesian approach and the MAP estimate is to be bayesian in a few parameters. For instance, instead of our approach where we maximize the likelihood of the validation set with respect to the precision parameter $\tau$, one could be bayesian and integrate over its empirical posterior distribution obtained within the MCMC. This would give us an estimate of how well the tasks share information with each other in the specific problem.
We leave these questions for future work.

@@

% Discuss overall result
% Fetch perplexity for each task and discuss how it improves results significantly for some tasks (less data?), and less larger data tasks.
% Give some advice on how to use this method in practice.

\begin{figure}[ht]
    \centering
    \resizebox{\linewidth}{!}{%
    \includegraphics[width=\textwidth]{figures/weights_vs_data_lengths.png}
    }
    \caption{The figure shows the L2-distance between each task's adapter weight and the global prior on the y-axis, and the number of training examples on the x-axis. We see that, as expected, tasks with more training data will have a larger distance to the global prior.}
    \label{fig:weights_vs_datalen} 
\end{figure}

\section{Conclusion}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
This paper presented a generalization of the LoRA fine-tuning method for multi-task problems, which we call the Hierarchical LoRA method. The hierarchical model allows tasks to share information between each other through a set of global hierarchical prior parameters, and can be seen as a generalization of the two conventional approaches for multi-task problems. We show that the Hierarchical LoRA model can improve the test perplexity for all tasks compared to both training the models independently and training one model for all tasks, and that it can mitigate the trade-off between the two approaches.
Future work includes investigating the effect that BoRA has on more tasks and datasets, investigating how the relative capacity of the global model affects the performance, and investigating the full posterior distribution of the model.

@@

\appendix
\section{Task specific test perplexities}
Table \ref{tbl:task_perplexities} shows the test perplexities for each task when using the hierarchical LoRA model with different precision hyperparameters $\tau$.

>>>>

\title{BoRA: Bayesian Hierarchical  Low-Rank Adaption for Multi-task Large Language Models}
\author[1]{Simen Eide}
\author[2]{Arnoldo Frigessi}
\affil[1]{University of Oslo, Schibsted}
\affil[1]{University of Oslo}
\date{March 2024}

@@

BoRA addresses these trade-offs by leveraging a Bayesian hierarchical model that allows tasks to share information through global hierarchical priors. This enables tasks with limited data to benefit from the overall structure derived from related tasks while allowing tasks with more data to specialize. Our experimental results show that BoRA outperforms both individual and unified model approaches, achieving lower perplexity and better generalization across tasks. This method provides a scalable and efficient solution for multi-task LLM finetuning, with significant practical implications for diverse applications.
}

\section{Introduction}
Large Language Models (LLM) have become a popular model for solving a wide range of generative text problems. LLMs are typically pretrained on a large and diverse dataset of texts, and then fine-tuned on a new data set of texts, dedicated to a specific task. The fine-tuning process is often done by maximizing the next token log likelihood of the task-specific dataset, and the resulting model is then used to make predictions and generations for new data. A popular fine-tuning method is Low-Rank Adaption (LoRA), which reduces the number of trainable parameters by a factor of up to 10'000 and the GPU memory requirement by a factor of 3, while still outperforming other fine-tuning techniques (\cite{hu_lora_2022}).

When performing fine-tuning of LLMs, the practitioner often wants to solve multiple similar tasks at the same time: 
A media organization might want to use an LLM to generate various textual elements to generate headlines, keywords, and summaries for a given news article. 
A website might have multiple chatbot tasks answering user inquiries across various topics.
And finally, a scriptwriting AI might want to generate dialogues for different characters in a movie, each with their unique style and vocabulary.

In these multi-task cases, the practitioner can either (1) train one model for each task and dataset separately, or (2) train one model for all tasks and condition the specific output wanted (e.g \cite{Raffel2019}).
There is a trade-off between these two approaches: Train each task separately and the model will be able to specialize on each task, but it may suffer when limited data are available for some task. Train one model for all tasks, and the model will be able to share information between tasks, but it may not be able to specialize on each task due to limited model capacity.

In this paper we suggest a way to circumvent these trade-offs and presents a generalization of the two LoRA fine-tuning methods for multi-task problems, which we call Bayesian Hierarchical Low-Rank Adaption method (BoRA).
The BoRA method allows tasks to share information between each other through sharing a set of global hierarchical prior parameters, in a Bayesian hierarchical setting. 
This means that tasks with little data can benefit from the global structure across related tasks, while tasks with more data can specialize on their specific task.
We show in Section \ref{sec:BoRA} that BoRA can be seen as a generalization of the two approaches above.

To test our method, we evaluate the BoRA on the next token generation problem of parliament speeches letting each parliament representative be a task. In our setting, BoRA is superior to both conventional approaches described above and suggests a way to mitigate the trade-off between the two.
% Write something about how easy it is to implement and how it can be used in practice?

The paper is organized as follows: Section \ref{sec:related_works} presents related works. Section \ref{sec:method} presents BoRA, the Hierarchical LoRA method; Section \ref{sec:experimental_setup} describes the experimental setup, Section \ref{sec:results} presents the results, and Section \ref{sec:discussion} discusses the results and the implications of the new method.

@@

\section{Related works} \label{sec:related_works}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
We group related work into two areas: multi-task learning and fine-tuning methods of large language models. Autoregressive LLMs and Bayesian modeling are described in Section \ref{sec:method}.

@@

\subsection{Finetuning methods}
A popular approach to finetuning neural networks involves adjusting only the top layer (or the n top layers) of a pre-trained neural network (e.g. \cite{yosinski_how_2014}). These techniques exploit that features learned in the lower layers of the network are general and transferable, while the top layers are more task-specific. This approach has been widely adopted in neural networks. However, in this paper we focus on the LoRA method, which instead allows us to train a low rank decomposition of the entire network.

There are several variations of the LoRA algorithm. The Sparse Mixture of Low Rank Adapters (SIRA) \cite{zhu_sira_2023}, for instance, creates a Mixture of Expert on the low-rank parameters. Another variation, the Weight Decomposed Low-Rank Adaption (DoRA) \cite{hayou_lora_2024}, decomposes the low-rank parameters into scale and unit norm direction parameters. There is also the Efficient Low Rank Adaption (LoRA+) \cite{hayou_lora_2024}, which improves the existing LoRA optimization algorithm by adjusting the learning rate of the low-rank parameters.
Lastly, MoRA \cite{jiang_mora_2024} decompose the low-rank parameters using learnable square matrices with non-parameter based compressions and decompressions.
All these methods are designed to improve the performance of language models similar to LoRA, and they can be used in conjunction with the proposed Bayesian Hierarchical LoRA method.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Method: Hierarchical LLM} \label{sec:method}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
This section describes the Hierarchical LoRA method for multi-task problems. 
We begin by defining the task and data structure, followed by an introduction to pretrained autoregressive language models. Next, we describe the LoRA method, and finally, we present the proposed Bayesian Hierarchical LoRA model.

\subsection{Task and Data Structure}
We define our study across $D$ distinct tasks, denoted by $d=1,2,...,D$. For each task $d$, we have a dataset $\mathcal{D}_d$ containing $N_d$ documents, with each document $n=1,..., N_d$ consisting of a sequence of $W_n$ tokens. This dataset structure can be formally represented as:

\begin{equation} \label{eq:data}
\mathcal{D} = \{ \mathcal{D}_d \}_{d=1}^D  =  \{ \{ w_{d,n,1:W_n} \}_{n=1}^{N_d} \}_{d=1}^D
\end{equation}
%
In this notation, $w_{d,n,1:W_n}$ represents the token sequence in the $n^{th}$ document of the $d^{th}$ task. For simplification in subsequent discussions, we will omit the indices $d$ and $n$ (and write $w_i$) when their reference is evident from the context.

@@

\subsection{The Bayesian Hierarchical LoRA model} \label{sec:BoRA}
In the hierarchical LoRA model, we introduce a LoRA parameter set for each task $d$, denoted as $\theta_d$, containing all the low-rank decomposition matricies $A_d$ and $B_d$ from each decomposed layer in the Large Language Model. The likelihood of the data $\mathcal{D}$ given the task parameters $\theta_{1:D}$ is then given by (combining equation \ref{eq:data} and \ref{eq:LLMprob}):

\begin{align}  \label{eq:lik}
    & \text{L}(\mathcal{D} | \theta_1, \theta_2, \ldots, \theta_D) = \prod_{d=1}^D L(\mathcal{D}_d | \theta_d) \nonumber \\
    &= \prod_{d=1}^D \prod_{n=1}^{N_d} \prod_{i=1}^{W_n-1} \text{LLM}(w_{d,n,i+1} | w_{d,n,1:i}; \theta_d).
\end{align}
%
%
Tasks will share some knowledge with each other, and we model this by introducing a Gaussian hierarchical prior over the task parameters $\theta_{1:D}$, given by
\begin{equation} \label{eq:prior}
    P(\theta_{1:D} | \Theta, \tau ) = \prod_{d=1}^D N(\theta_d ; \Theta, \frac{1}{\tau} I)
\end{equation}
%
where $\Theta$ is a set of hierarchical mean parameters, $I$ is a unit diagonal matrix and $\tau \geq 0$ is a scalar precision hyperparameter controlling how similar the task parameters $\theta_d$ should be to the hierarchical mean parameters $\Theta$.
We let $\Theta$ have a uniform hyperprior (i.e. $P(\Theta) = 1$). The prior assumes that the task parameters share a common origin from the common Gaussian prior, because the tasks are related: input data come from similar distributions and the output tasks have similar aspects. 
The precision hyperparameter $\tau$ controls how much the task parameters $\theta_d$ are a priori expected to be allowed to deviate from the hierarchical mean parameters $\Theta$. 
This is a measure for how much structure and information the tasks share with each other, and should be set by the practitioner based on her's prior knowledge.

@@

The resulting BoRA model solves each task based on its data size and similarity to the other tasks: If a task has few data points, the posterior in equation \ref{eq:posterior} will be dominated by the prior term and the task parameters will be close to the global hierarchical parameters and borrow information and structure from these. On the other hand, if a task has a lot of data points, the likelihood will dominate the posterior and the task parameters will be allowed to learn more about the specific task and rely less on the hierarchical parameters.

@@

\subsection{Optimization}
Given the precision hyperparameter $\tau$, we want to find the maximum a posteriori (MAP) estimate of the hierarchical model. 
We will do this by using AdamW (\cite{adamW}), a gradient-based optimization algorithm, optimizing over the task parameters $\theta_{1:D}$ and the hierarchical mean parameters $\Theta$ using the posterior in equation \ref{eq:posterior}.
This implies that the task parameters with have gradients both towards minimizing the convential LLM loss (represented by the likelihood term) and the hierarchical mean parameters (originating from the prior). The hierarchical mean parameters $\Theta$ will have gradients towards the average of the task parameters, and learn to represent the global structure of the tasks.

@@

    \centering
    \resizebox{\linewidth}{!}{%
    \includegraphics[width=\textwidth]{figures/training_lengths.png}
    }
    \caption{Number of training examples for each task.}
    \label{fig:task_len}
\end{figure}
% As base model, use opt-350m as it is predominantly trained on English, and only has seen a small amount of Norwegian data from the commoncrawls dataset.
To test our method, we optimize the model with a range of different precision hyperparameters $\tau$, and evaluate the perplexity on the test set for each task.
% DEF PERPLEXITY
Perplexity is defined as the exponentiated average negative log-likelihood per token, and is a common metric for evaluating language models. A lower perplexity indicates a higher likelihood and a better model.
We use the Talk of Norway Dataset~\cite{lapponi_talk_2018}, which consists of speeches of Norwegian parliament politicians.
Speakers come from different political parties and geographical areas, but the tasks will still share a common domain, represented by parliamentary speeches in Norway over a short period of time. 
Therefore, we can consider different speakers of this dataset as different tasks. Specifically, we select chronologically the 25 first speakers that have above 100 speeches in the dataset.
This gives us a total of 25 tasks with samples ranging from 110 to 477 documents, and an average of 202 documents per task. For some speakers we have significantly less data compared to others. 
The distribution of samples per task can be seen in Figure~\ref{fig:task_len}.
We leave 33\% of the data for the test set.

@@

We find no relationship between dataset size and the final perplexity (Figure \ref{fig:absolute_improvement}). One could expect that tasks with more data are able to learn more about their specific task and achieve a lower perplexity, but this is not the case in our experiments. There are many other task specific factors such as under-represented dialects and political views that can influence the final perplexity. Controlling for these factors is difficult and out of scope for this paper, but we believe that these factors may be the reason for this result.

@@

%% MCMC vs MAP
In principle, one could adopt a fully Bayesian approach, instead than the Maximum a Posteriori maximization, which would tell us how much we can trust the hierarchical model. Such an approach  would require the use of Markov Chain Monte Carlo (MCMC), Variational Inference or other methods.
This would require to sample from the posterior distribution of the hierarchical model, and would allow to obtain uncertainty estimates for the task parameters.
However, MCMC methods are computationally heavy, and it is not clear to us how to best sample from the posterior distribution of the language model in an efficient and scalable way.
A middle ground between a full Bayesian approach and the MAP estimate is to be Bayesian for a few parameters. For instance, instead of our approach where we maximize the likelihood of the validation set with respect to the precision parameter $\tau$, one could be Bayesian and integrate over its empirical posterior distribution obtained from the MCMC. This would give us an estimate of how well the tasks share information with each other in the specific problem.
We leave these questions for future work.

\begin{figure}[ht]
    \centering
    \resizebox{\linewidth}{!}{%
    \includegraphics[width=\textwidth]{figures/weights_vs_data_lengths.png}
    }
    \caption{The figure shows the L2-distance between each task's adapter weight and the global prior on the y-axis, and the number of training examples on the x-axis. We see that, as expected, tasks with more training data  have a larger distance to the global prior.}
    \label{fig:weights_vs_datalen} 
\end{figure}

@@

\section{Conclusion}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
This paper presented a new generalization of the LoRA fine-tuning method for multi-task problems, which we call BoRA,  Bayesian Hierarchical Low-Rank Adaption for Multi-task
Large Language Models. The hierarchical model allows tasks to share information between each other through a set of global hierarchical prior parameters, and can be seen as a generalization of the two conventional approaches for multi-task problems. We show that BoRA can improve the test perplexity for all tasks compared to both training the models independently and training one model for all tasks, and that it can mitigate the trade-off between the two approaches. We propose to adapt the learning rate to the design parameter that controls the trade off between likelihood and prior. 
Future work includes investigating the effect that BoRA has on more tasks and datasets, investigating how the relative capacity of the global model affects the performance, and investigating the full posterior distribution of the model.

@@

\appendix
\section{Task specific test perplexities}
Table \ref{tbl:task_perplexities} shows the test perplexities for each task when using BoRA with different precision hyperparameters $\tau$.
